workshop

### 2022-09-16 scripts/workshop/workshop.Rmd
updating supp 1

species_comp %>% ggplot(.,aes(x=reorder(abb_name, mean), y=mean)) + geom_point() + geom_linerange(aes(ymin=mean-se,ymax=mean+se)) + theme(axis.text.x = element_text(angle = 30, hjust = 1))

>>>>

vl %>% ggplot(.,aes(x=reorder(abb_name, mean), y=mean)) + geom_point() + geom_linerange(aes(ymin=mean-se,ymax=mean+se)) + theme(axis.text.x = element_text(angle = 30, hjust = 1))
